Best Practices for Alchemical Free Energy Calculations: v\versionnumber

### 2020-01-14 paper/manuscript.tex
adding changes to cleanup of sec 4

\begin{equation}
    \Delta G_{\mathrm{bind}} = -RT\ln\frac{\int_\mathrm{bound} \exp(-\beta U(\mathbf{x}))d\mathbf{x}}{\int_\mathrm{unbound} \exp(-\beta U(\mathbf{x}))d\mathbf{x}}
\end{equation}
Or more generally in a simplified form the free energy difference between the bound and unbound states is:
\begin{equation}
\Delta f \equiv f(\mathrm{bound}) - f(\mathrm{unbound}) = -\ln\frac{Z(\mathrm{unbound})}{Z({\mathrm{bound}})},
\end{equation}
where $Z = \int_\mathrm{bound} \exp(-\beta U(\mathbf{x}))d\mathbf{x}$ represents the configurational integral. 
How can we compute $\Delta G_{\mathrm{bind}}$ from a molecular dynamics simulation? Running a direct simulation of the binding events is too computationally costly, meaning we cannot easily estimate the configurational integrals of the bound and unbound state from the simulation. This is where alchemical free simulations come in. We can write down a thermodynamic cycle as seen in ~\ref{fig:fig_binding_thermodynamic_cycle}, for a relative free energy simulation. Based on this cycle we can compute the relative free energy of binding between two compounds $A$ and $B$, by going along the arrow of $\Delta G_{\mathrm{bound}}$, where we introduce a second compound that is similar to the first one. Now $\Delta G_{\mathrm{bound}}$ can be expressed as a ratio of partition functions of toluene (A) and benzyl alcohol (B). 
The defining characteristic of alchemical free energy calculations is the use of a series of alchemically-modified potential functions $U(x; \lambda)$ in which an alchemical parameter $\lambda$ modulates interactions in a manner that cannot occur in real chemical systems.
One or more simulations are used to collect data from a multitude of alchemical states to compute a free energy difference between a chemical state ($\lambda_0$) and another chemical or alchemical reference state ($\lambda_1$),
\begin{eqnarray}
\Delta f &\equiv& f(\lambda_1) - f(\lambda_0) = - \ln \frac{Z(\lambda_1)}{Z(\lambda_0)} , \label{equation:dimensionless-free-energy-difference}
\end{eqnarray}
where the dimensionless free energy $f(\lambda) \equiv \beta F(\lambda)$ is given in terms of partition functions $Z(\lambda)$,
\begin{eqnarray}
Z(\lambda) &=& \int dx \, e^{-u(x; \lambda)} .
\label{equation:partition-function-definition}
\end{eqnarray}
Here, the inverse thermal energy $\beta \equiv (k_B T)^{-1}$ where $k_B$ is the Boltzmann constant and $T$ is the absolute temperature, and the \emph{reduced potential} $u(x; \lambda)$~\cite{shirts2008statistically} is generally given by a trace over thermodynamic parameters with their conjugate dynamical variables,
\begin{eqnarray}
u(x;\lambda) &\equiv& \beta \left[ U(x;\lambda) + p \, V(x) + \sum_{i=1}^N \mu_i \, N_i(x) + \cdots \right] . \label{equation:reduced-potential}
\end{eqnarray}
Here, the collection of thermodynamic and alchemical parameters $\theta \equiv \{\beta, \lambda, p, \mu, \ldots\}$ defines a \emph{thermodynamic state}.
The physical transformation of interest---such as a protein-ligand association process, or transfer free energy among phases---may involve a thermodynamic cycle that requires several free energy differences $\Delta f$ to be computed in order to produce an estimate of the overall desired quantity.

@@

It is expected that AFE methods can provide a valuable tool for drug discovery, capable of outperforming alternative approaches~\cite{kuhn2017prospective}. It has been stressed that successful application in industry requires more knowledge of the "domain of applicability", in other words, a greater understanding of the success and failure~\cite{sherborne2016collaborating}, which in turn requires robust protocols for preparing, submitting and analysing AFE calculations. In this regard, the issues mentioned in the previous section such as understanding the suitability and timescales to capture the structure activity relationships (SAR), and performing up-front tests of performance are all relevant to drug discovery applications. Without venturing too far into details of system setup, which is beyond the scope of this article, there are some points to be stressed. 

@@

The calculations aim to capture the alchemical change from one ligand to another as accurately as possible. Therefore, it is necessary to consider details of the experimental setup, such as pH. Biological assays are usually run at neutral pH but this is not always the case, and protein and ligand preparation protocols should reflect this. In more detail, the formal charge, or tautomeric state of the small molecules can change within a series of analogs. The change of pKa is a common medicinal chemistry strategy to modify drug properties and would normally require explicit effort to incorporate into alchemical calculations. Further concerns about the experimental setup require understanding what protein construct is used in the bioassay. For instance, does the X-ray that is to be used for the calculations match the construct used for screening (i.e. catalytic vs full length, monomer vs dimer etc) (CITE https://www.nature.com/articles/s41598-018-23039-5)? Also, were certain co-factors or partner proteins required in the bioassay? 

@@

As also mentioned, good performance of alchemical FE calculations requires an accurate representation of the ligand binding mode, normally solved via X-ray crystallography. If more than one structure is available, the modeler should pay attention to choose the most suitable. The quality of the structure can be a concern, and the reader is referred to work of Warren et al. for a detailed discussion of choosing optimal structures for structure-based modeling~\cite{warren2012essential}. It is also useful to study the structure activity relationship and understand the expected impact in the binding site, is side chain movement required and is there evidence of this in any alternative X-ray structures of the same protein? Normally, only one protein and water configuration is used for a series of alchemical FE calculations, so this needs to be capable of accommodating the smallest through to largest ligands in a way that allows stable and well behaved simulations. This can be a practical limitation for the alchemical changes that are feasible, a simple work-around can be to separate compounds into sub-series for different calculations. If multiple structures are available there is some evidence the higher affinity complex can give better performance~\cite{perez-benito2019predicting}.
\subsection{Input setup and scale of calculations}
In a drug discovery setting it is normal to consider dozens (or more) of ligands and it is necessary to align them in the binding site. There is no detailed study of how different alignment approaches may affect results, but the user should be aware of some practical considerations. Tools are available to compare the ligands and build the hybrid topologies that define the changes between one ligand and another~\cite{loeffler2015fesetup,hedges2019biosimspace,gapsys2015pmx}. In simple terms, providing poor alignment to these tools will make this job harder. Therefore, docking ligands with no restraints is not usually the best method for defining the ligand inputs, instead a core restrained docking can provide satisfactory outcomes, but in this case one still should pay careful attention to consistency of alignment for identical substituents. Another alternative is to manually edit the same core with the changing substituents. This provides assurances that coordinates for the non-perturbed structures remain identical and aromatic substituents for instance obey consistent dihedral angles but is not feasible for many compounds and therefore automation can be desirable. Finally, the role of water in ligand binding is now well understood and it can be crucial to capture the changes in binding site solvation during ligand binding. Can crystallographic waters be retained? Do they clash with some of the larger ligands used in the FEP? If so, how will the water be incorporated for smaller ligands that require the water – consider pre-solvation methods such as GCMC steps~\cite{michel2010prediction}. Other tools such as watermap or opensource equivalents (SSTmap, others) can be used to define water structure for systems with no experimental evidence of water sites. Before launching large numbers of alchemical free energy calculations it is recommended to test the system using classical MD simulations and limited numbers of alchemical perturbations. Metrics such as ligand and protein RMSD and RMSF can be inspected, along with visual inspection of simulations, to ensure the system is stable and likely to be suitable for FE calculations. 
Running binding FE calculations in a drug discovery application will typically require the use of software or tools to facilitate the calculations of many compounds. The commercial implementation from Schr\"{o}dinger, FEP+, uses a graphical user interface and once the user has calculated any missing force field parameters, calculations can be prepared and submitted within minutes. The software builds the network of perturbations, connecting similar compounds based on LOMAP methodology~\cite{liu2013lead}, all inputs for the Desmond simulations are built automatically and the job can be saved or run immediately on available GPUs. The cost of this software is often prohibitive but alternative tools are becoming available to allow relatively straight forward running of alchemical FE calculations with other software~\cite{gapsys2015pmx, loeffler2015fesetup, song2019using, gapsys2020large,  jespers2019qligfep}. One consideration at this point is to define the perturbations suitable for the application. For instance, if the goal is to accurately assess the relative binding energy of a small number of compounds, possibly with challenging synthesis, the map of perturbations may contain as many connections between compounds as affordable. However, when running calculations on hundreds of compounds a so called ‘star-map’ can be used that just contains one connection per compound: perturbing every compound to a central ligand, typically the crystal structure ligand~\cite{konze2019reactionbased}. In this way the top-ranking examples can be readily identified and submitted to additional calculations in a second round. 
\subsection{Making predictions, understanding errors}
\label{subsec:predictions}
For prospective drug discovery applications there are several other considerations including understanding likely errors and taking selection bias into account. It is crucial when proposing compounds for synthesis to have some idea of the underlying error or uncertainty in the predictions. A retrospective assessment can give an indication of prospective performance for similar molecules~\cite{ciordia2016application}. Beyond this, several parameters provide useful indicators of performance, results suggest MBAR errors for perturbations greater than 0.3 kcal/mol can be indicative of inaccuracy~\cite{perez-benito2019predicting}. In addition, the hysteresis can be checked by comparing the difference for forward and reverse perturbations of the same structural change, or in the case of large maps of perturbations cycle closure hysteresis~\cite{wang2013modeling} indicates problematic perturbations involved in cycles connecting many compounds. Selection bias, as described above, can be problematic in prospective applications as there is normally an aim to focus on only a narrow range of predicted activity (i.e. the most active). Thus, correlation between prediction and subsequent experiment may lead to disappointment but corrections can be applied based on previous recommendations~\cite{abel2017critical}. 
In summary, the successful use of alchemical calculations in drug discovery requires working in the domain of applicability, using a high quality X-ray structure of the target compounds, and testing the approach retrospectively to ensure the system setup is well-behaved. Always assess the confidence in the predictions and communicate this when discussing with experimentalists. Consider performing repeat calculations for at least some of the perturbations in the study. In a drug discovery setting it is inevitable to consider larger virtual libraries, in these cases again evaluate if shorter simulation time per $\lambda$ window can be sufficient for a ‘virtual screening’ mode of application. It is expected that future tools may allow efficient exploration of large virtual libraries. There are many accounts of success of alchemical FE calculations, the methods show good performance towards the goal of binding energy prediction. However, it is important to have realistic expectations. Structure based drug design projects are often capable of improving potency relatively quickly and the range of activity narrows to just two-to-three log units. It may seem hard to impact with substantially different, more potent, stand-out compounds in this scenario, but binding energy prediction can still be extremely useful for ensuring activity is maintained as other properties are optimized. An interesting cost benefit analysis has shown the value of activity prediction, see discussion above and articles such as~\cite{mobley2012perspectiv}. From a drug discovery point of view, FEP is expanding its domain of applicability, there are reports of success using homology models and GPCRs for instance, as well as enabling charge change and scaffold hopping, but these systems are undoubtedly more difficult.  In the meantime, the use cases are expanding to resistance prediction, disease mutation prediction, solubility prediction – an exciting future for alchemical FE calculations. 

@@

\section*{Author Contributions}
%%%%%%%%%%%%%%%%
% This section mustt describe the actual contributions of
% author. Since this is an electronic-only journal, there is
% no length limit when you describe the authors' contributions,
% so we recommend describing what they actually did rather than
% simply categorizing them in a small number of
% predefined roles as might be done in other journals.
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io
% for more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%%
\todo[inline, color={green!20}]{ASJSM: @everyone, can you check your contribution is acknowledge and if not add the appropriate information. }
(Explain the contributions of the different authors here)
ASJSM: Coordinated the document, contributed to most sections, and co-designed figures ~\ref{} and created figures \ref{fig:fig_what_is_lambda},~\ref{fig:fig1_what_is_alchemy},~\ref{fig:overlap} and replotted~\ref{fig:automatic-equilibration-detection} and improved ~\ref{fig:fig_types_of_networks}.
JS: created figures \ref{fig:fig_what_is_alchemy},~\ref{fig:fig_binding_thermodynamic_cycle},~\ref{fig:fig_topology},~\ref{fig:fig_mcss},~\ref{fig:fig_types_of_networks},~\ref{fig:fig_absolute_thermodynamic_cycle},~\ref{fig:scatterplot_analysis}, the data representation section, the checklist and contributed to general formatting discussions and editing.
MK: Contributed to the Data Analysis section, provided the data for figure~\ref{fig:overlap} and helped edit the paper.
DLM: Contributed to the outline, drafted some of the sections, gave ideas on figures, and helped edit the paper.
GT: Contributed to introduction and drug discovery sections, and helped edit the paper.
AR: Created figure~\ref{fig:freeenergytrajectories}, contributed to section \ref{sec:step2}, and helped edit the paper.
MRS: Helped create figure~\ref{fig:fig_what_is_lambda}, wrote sections describing choices for alchemical pathways and analysis for free energy calculations.
LNN: Helped write the simulation length, stopping conditions, and information saving section.
BA: \todo[inline, color={red!20}]{@Bryce insert info here}
JM: Contributed to sections~\ref{subsec:reproducible},~\ref{sec:step1},~\ref{} 4.2, 5.3, 6, 8.3.1, 8.3.2\
JDC: \todo[inline, color={red!20}]{@JDC insert info here}
HX: Contributed section~\ref{subsec:accuracy}, to section~\ref{sec:relative-fe-protocol}, and to section~\ref{sec:are-they-good}.

>>>>

\begin{equation}
    \Delta G_{\mathrm{bind}} = -RT\ln\frac{\int_\mathrm{bound} \exp(-\beta U(\mathbf{x}))d\mathbf{x}}{\int_\mathrm{unbound} \exp(-\beta U(\mathbf{x}))d\mathbf{x}}
\end{equation}
Or more generally in a simplified form the free energy difference between the bound and unbound states is:
\begin{equation}
\Delta f \equiv f(\mathrm{bound}) - f(\mathrm{unbound}) = -\ln\frac{Z(\mathrm{unbound})}{Z({\mathrm{bound}})},
\end{equation}
where $Z = \int_\mathrm{bound} \exp(-\beta U(\mathbf{x}))d\mathbf{x}$ represents the configurational integral. 
How can we compute $\Delta G_{\mathrm{bind}}$ from a molecular dynamics simulation? Running a direct simulation of the binding events is too computationally costly, meaning we cannot easily estimate the configurational integrals of the bound and unbound state from the simulation. This is where alchemical free energy simulations come in. We can write down a thermodynamic cycle as seen in ~\ref{fig:fig_binding_thermodynamic_cycle}, for a relative free energy simulation. Based on this cycle we can compute the relative free energy of binding between two compounds $A$ and $B$, by going along the arrow of $\Delta G_{\mathrm{bound}}$, where we introduce a second compound that is similar to the first one. Now $\Delta G_{\mathrm{bound}}$ can be expressed as a ratio of partition functions of toluene (A) and benzyl alcohol (B). 
The defining characteristic of alchemical free energy calculations is the use of a series of alchemically-modified potential functions $U(x; \lambda)$ in which an alchemical parameter $\lambda$ modulates interactions in a manner that cannot occur in real chemical systems.
One or more simulations are used to collect data from a multitude of alchemical states to compute a free energy difference between a chemical state ($\lambda_0$) and another chemical or alchemical reference state ($\lambda_1$),
\begin{eqnarray}
\Delta f &\equiv& f(\lambda_1) - f(\lambda_0) = - \ln \frac{Z(\lambda_1)}{Z(\lambda_0)} , \label{equation:dimensionless-free-energy-difference}
\end{eqnarray}
where the dimensionless free energy $f(\lambda) \equiv \beta F(\lambda)$ is given in terms of partition functions $Z(\lambda)$,
\begin{eqnarray}
Z(\lambda) &=& \int dx \, e^{-u(x; \lambda)} .
\label{equation:partition-function-definition}
\end{eqnarray}
Here, the inverse thermal energy $\beta \equiv (k_B T)^{-1}$ where $k_B$ is the Boltzmann constant and $T$ is the absolute temperature, and the \emph{reduced potential} $u(x; \lambda)$~\cite{shirts2008statistically} is generally given by a trace over thermodynamic parameters with their conjugate dynamical variables,
\begin{eqnarray}
u(x;\lambda) &\equiv& \beta \left[ U(x;\lambda) + p \, V(x) + \sum_{i=1}^N \mu_i \, N_i(x) + \cdots \right] . \label{equation:reduced-potential}
\end{eqnarray}
Here, the collection of thermodynamic and alchemical parameters $\theta \equiv \{\beta, \lambda, p, \mu, \ldots\}$ defines a \emph{thermodynamic state}.
The physical transformation of interest---such as a protein-ligand association process, or transfer free energy among phases---may involve a thermodynamic cycle that requires several free energy differences $\Delta f$ to be computed in order to produce an estimate of the overall desired quantity.

@@

Many practitioners expect AFE methods to provide valuable guidance for drug discovery, and to exhibit accuracy superior to most  alternative approaches for suitable targets~\cite{kuhn2017prospective}. It has been stressed that successful application in industry may require considerable knowledge of the "domain of applicability" of free energy calculations -- where they work well and where they will not ~\cite{sherborne2016collaborating}. Successful application also requires robust protocols for preparing, submitting and analysing AFE calculations. In this regard, the issues mentioned in the previous section such as understanding the suitability and timescales to capture the structure activity relationships (SAR), and performing up-front tests of performance are all relevant to drug discovery applications. Without venturing too far into details of system setup, which is beyond the scope of this article, we highlight some critical factors affecting accuracy and successful application. 

@@

The calculations aim to capture the alchemical change from one ligand to another as accurately as possible. Therefore, it is necessary to consider details of the experimental setup, such as pH. Biological assays are usually run at neutral pH but this is not always the case, and protein and ligand preparation protocols should reflect this. In more detail, the formal charge, or tautomeric state of the small molecules can change within a series of analogs. The change of pKa is a common medicinal chemistry strategy to modify drug properties and would normally require explicit effort to incorporate into alchemical calculations. Also, to ensure modeling matches experiment, we need to ensure that we simulate the same system -- which requires understanding what protein construct is used in the bioassay. For instance, does the X-ray that is to be used for the calculations match the construct used for screening (i.e. catalytic vs full length, monomer vs dimer etc) (CITE https://www.nature.com/articles/s41598-018-23039-5)? Also, were certain co-factors or partner proteins required in the bioassay? 

@@

As also mentioned, good performance of alchemical FE calculations requires an accurate representation of the ligand binding mode, which often is estimated based on X-ray crystallography for a related ligand. If more than one structure is available, the modeler should pay attention to choose the most suitable. The quality of the structure can be a concern, and the reader is referred to work of Warren et al. for a detailed discussion of choosing optimal structures for structure-based modeling~\cite{warren2012essential}. It is also useful to study the structure activity relationship and understand the expected impact in the binding site, whether side chain movement in the protein will be required, and whether there evidence of this in any alternative X-ray structures of the same protein. Often, only one protein and water configuration is used for a series of alchemical FE calculations, so this needs to be capable of accommodating the smallest through to largest ligands in a way that allows stable and well behaved simulations. This can be a practical limitation for the alchemical changes that are feasible, though a simple work-around can be to separate compounds into sub-series for different calculations. If multiple structures are available there is some evidence the higher affinity complex can give better performance~\cite{perez-benito2019predicting}, at least in some cases. However, ligands and proteins can also undergo unexpected changes in binding mode for related ligands, which can make these issues more complex to deal with.

\subsection{Input setup and scale of calculations}
In a drug discovery setting it is normal to consider dozens (or more) of ligands and it is necessary to align them in the binding site. There is no detailed study of how different alignment approaches may affect results, but the user should be aware of some practical considerations. Tools are available to compare the ligands and build the hybrid topologies that define the changes between one ligand and another~\cite{loeffler2015fesetup,hedges2019biosimspace,gapsys2015pmx}. In simple terms, providing poor alignment to these tools will make this job harder. Therefore, docking ligands with no restraints is not usually the best method for defining the ligand inputs, instead a core restrained docking can provide satisfactory outcomes, but in this case one still should pay careful attention to consistency of alignment for identical substituents. Another alternative is to manually edit the same core with the changing substituents. This provides assurances that coordinates for the non-perturbed structures remain identical and aromatic substituents for instance obey consistent dihedral angles but is not feasible for many compounds and therefore automation can be desirable.

Finally, the role of water in ligand binding is now well understood and it can be crucial to capture the changes in binding site solvation during ligand binding. Can crystallographic waters be retained? Do they clash with some of the larger ligands used in the FEP? If so, how will the water be incorporated for smaller ligands that require the water – consider pre-solvation methods such as GCMC steps~\cite{michel2010prediction}. Other tools such as WaterMap or open source equivalents (SSTmap, others) can be used to define water structure for systems with no experimental evidence of water sites. Before launching large numbers of alchemical free energy calculations it is recommended to test the system using classical MD simulations and limited numbers of alchemical perturbations. Metrics such as ligand and protein RMSD and RMSF can be inspected, along with visual inspection of simulations, to ensure the system is stable and likely to be suitable for FE calculations.

Running binding FE calculations in a drug discovery application will typically require the use of software or tools to facilitate the calculations of many compounds. The commercial implementation from Schr\"{o}dinger, FEP+, uses a graphical user interface and once the user has calculated any missing force field parameters, calculations can be prepared and submitted within minutes. The software builds the network of perturbations, connecting similar compounds based on LOMAP methodology~\cite{liu2013lead}, all inputs for the Desmond simulations are built automatically and the job can be saved or run immediately on available GPUs. The cost of this software is often prohibitive but alternative tools are becoming available to allow relatively straight forward running of alchemical FE calculations with other software~\cite{gapsys2015pmx, loeffler2015fesetup, song2019using, gapsys2020large,  jespers2019qligfep}. One consideration at this point is to define the perturbations suitable for the application. For instance, if the goal is to accurately assess the relative binding energy of a small number of compounds, possibly with challenging synthesis, the map of perturbations may contain as many connections between compounds as affordable. However, when running calculations on hundreds of compounds a so called ‘star-map’ can be used that just contains one connection per compound: perturbing every compound to a central ligand, typically the crystal structure ligand~\cite{konze2019reactionbased}. In this way the top-ranking examples can be readily identified and submitted to additional calculations in a second round. 
%
\subsection{Making predictions, understanding errors}
\label{subsec:predictions}
For prospective drug discovery applications there are several other considerations including understanding likely errors and taking selection bias into account. It is crucial when proposing compounds for synthesis to have some idea of the underlying error or uncertainty in the predictions. A retrospective assessment can give an indication of prospective performance for similar molecules~\cite{ciordia2016application}. Beyond this, several parameters provide useful indicators of performance. Results suggest MBAR errors greater than 0.3 kcal/mol for perturbations can be indicative of inaccuracy~\cite{perez-benito2019predicting}. In addition, the hysteresis can be checked by comparing the difference for forward and reverse perturbations of the same structural change, or in the case of large maps of perturbations cycle closure errors~\cite{wang2013modeling} indicate problematic perturbations involved in cycles connecting many compounds. Selection bias, as described above, can be problematic in prospective applications as there is normally an aim to focus on only a narrow range of predicted activity (i.e. the most active). Thus, correlation between prediction and subsequent experiment may lead to disappointment but corrections can be applied based on previous recommendations~\cite{abel2017critical}.

In summary, the successful use of alchemical calculations in drug discovery requires working in the domain of applicability, using a high quality X-ray structure of the target compounds, and testing the approach retrospectively to ensure the system setup is well-behaved. Always assess your confidence in the resulting predictions and communicate this when discussing with experimentalists. Consider performing repeat calculations for at least some of the perturbations in the study. In a drug discovery setting it is inevitable to consider larger virtual libraries. In these cases again evaluate if shorter simulation time per $\lambda$ window can be sufficient for a ‘virtual screening’ mode of application. It is expected that future tools may allow efficient exploration of large virtual libraries. There are many accounts of success of alchemical FE calculations, the methods show good performance towards the goal of binding energy prediction. However, it is important to have realistic expectations.

Structure based drug design projects are often capable of improving potency relatively quickly, even with only limited application of computational approaches and the range of activity narrows to just two-to-three log units. It may seem hard to have impact with substantially different, more potent, stand-out compounds in this scenario, but binding energy prediction can still be extremely useful for ensuring activity is maintained as other properties are optimized. An interesting cost benefit analysis has shown the value of activity prediction, see discussion above and articles such as~\cite{mobley2012perspectiv}. From a drug discovery point of view, FEP is expanding its domain of applicability, and there are reports of success using homology models and GPCRs for instance, as well as enabling charge change and scaffold hopping, but these systems are undoubtedly more difficult.  In the meantime, the use cases are expanding to resistance prediction, disease mutation prediction, solubility prediction – an exciting future for alchemical FE calculations. 

@@

\section*{Author Contributions}
%%%%%%%%%%%%%%%%
% This section mustt describe the actual contributions of
% author. Since this is an electronic-only journal, there is
% no length limit when you describe the authors' contributions,
% so we recommend describing what they actually did rather than
% simply categorizing them in a small number of
% predefined roles as might be done in other journals.
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io
% for more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%%
\todo[inline, color={green!20}]{ASJSM: @everyone, can you check your contribution is acknowledge and if not add the appropriate information. }
(Explain the contributions of the different authors here)
ASJSM: Coordinated the document, contributed to most sections, and co-designed figures ~\ref{} and created figures \ref{fig:fig_what_is_lambda},~\ref{fig:fig1_what_is_alchemy},~\ref{fig:overlap} and replotted~\ref{fig:automatic-equilibration-detection} and improved ~\ref{fig:fig_types_of_networks}.
JS: created figures \ref{fig:fig_what_is_alchemy},~\ref{fig:fig_binding_thermodynamic_cycle},~\ref{fig:fig_topology},~\ref{fig:fig_mcss},~\ref{fig:fig_types_of_networks},~\ref{fig:fig_absolute_thermodynamic_cycle},~\ref{fig:scatterplot_analysis}, the data representation section, the checklist and contributed to general formatting discussions and editing.
MK: Contributed to the Data Analysis section, provided the data for figure~\ref{fig:overlap} and helped edit the paper.
DLM: Contributed to the outline, drafted some of the sections, gave ideas on figures, and helped edit the paper.
GT: Contributed to introduction and drug discovery sections, and helped edit the paper.
AR: Created figure~\ref{fig:freeenergytrajectories}, contributed to section \ref{sec:step2}, and helped edit the paper.
MRS: Helped create figure~\ref{fig:fig_what_is_lambda}, wrote sections describing choices for alchemical pathways and analysis for free energy calculations.
LNN: Helped write the simulation length, stopping conditions, and information saving section.
BA: Helped write the uncertainty estimation, stopping conditions, and output analysis sections and created figure ~\ref{fig:convergence_forward_reverse}.
JM: Contributed to sections~\ref{subsec:reproducible},~\ref{sec:step1},~\ref{} 4.2, 5.3, 6, 8.3.1, 8.3.2\
JDC: \todo[inline, color={red!20}]{@JDC insert info here}
HX: Contributed section~\ref{subsec:accuracy}, to section~\ref{sec:relative-fe-protocol}, and to section~\ref{sec:are-they-good}.
